Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-04-05 paper/paper.qmd
minor fix

@@

For each treatment, we selected 30 different people (n = 30).
Through randomly picking the virtual citizens, we replicated 30 experimental units per treatment.
The even observations per treatment group ensures we have a balanced design.

@@

1. The median scores vary by both drug type and dosage level.
2. Tramadol (high dosage) appears to have a wider spread in scores compared to other groups.
3. The Placebo groups, both low and high dosage, show relatively similar median scores.
4. There is noticeable variability within each drug type, with some groups showing larger interquartile ranges (IQR) than others.
5. The boxplots indicate potential outliers in several groups, as shown by individual points beyond the whiskers.

These boxplots provide an initial comparison of cognitive performance across drug types and dosages, highlighting both central tendency and variability in memory game scores.

>>>>

This study followed all four principles of experimental design: **Control, Block, Randomization and Replication**.

@@

For each treatment, we selected 30 different people (n = 30).
Through randomly picking the virtual citizens, we **replicated** 30 experimental units per treatment.
The even observations per treatment group ensures we have a balanced design.

@@

1. The median scores for all drugs appear similar before treatment.
2. Tramadol has a higher median than other drugs both before and after treatment.
3. The Placebo group has a slightly lower median score compared to other drugs.
4. There is one outlier in the Tramadol group before treatment.
5. The (IQR) is similar across all drug types, though Tramadol sees a decrease in its
IQR in the memory game scores after treatment.
These boxplots provide an initial comparison of cognitive performance changes before and after
drug administration.
